### 2012-01-23 trunk/GUIErrorDetector/paper/abstract.tex
paper revise

\begin{abstract}
Graphical User Interface (GUI) is a critical component of today's software.
 It provides user-friendly access to the functionality provided by the application.
To keep GUIs responsive and active, a GUI application often spawns
 separate threads to handle lengthy operations in the background,
such as expensive computations, I/O tasks, and network requests.
However, many modern GUI frameworks require all GUI objects
must be accessed exclusively by the \textit{event dispatching thread}
(or called \textit{UI thread}). If a GUI object
is accessed through a non-UI thread, an \textit{invalid thread access} error
occurs and the whole application may abort consequently.

In this paper, we present a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph
reachability problem. Our technique starts from call graph entry nodes to
statically explore all possible paths that may cause a non-UI thread
to access a GUI object.
However, the heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms insufficient to build a both complete and precise
call graph. Thus, we present a combined RTA and k-CFA
call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms, namely SWT, Eclipse plugin development framework, Java Swing, and Android. In an evaluation
on XX subjects over XXX LOC, our technique found a number of real-world errors,
suggesting its effectiveness and showing good scalability.

>>>>

\begin{abstract}
To keep a Graphical User Interface (GUI) responsive and active, a GUI
application often has a main \textit{UI thread} (or \textit{event dispatching thread})
and spawns separate threads to handle lengthy operations in the background,
such as expensive computation, I/O tasks, and network requests.
Many GUI frameworks require all GUI objects to be accessed exclusively by the
UI thread. If a GUI object is accessed through a non-UI thread,
an \textit{invalid thread access} error occurs and the whole
application may abort.

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms fail to build a good
call graph. Thus, we present a method to overcome the limitations, and
build reflection-aware call graphs.

%call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms: SWT, Eclipse plugin development framework, Java Swing, and
Android. In an evaluation on XX subjects over XXX LOC, our technique
found a number of real-world errors, suggesting its effectiveness
and showing good scalability.

### 2012-01-23 trunk/GUIErrorDetector/paper/evaluation.tex
paper revise

We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
market as evaluation subjects. We choose subjects for each supported GUI framework
as follows. We search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and select subjects based on the following
criterias: first, the subject must be a multithread GUI application, not
an open library. Second, the subject must undergone at least two years of active development,
and is listed in the first 3 results pages based on popularity. This permits us
to exclude all pre-mature subjects, which may contain obvious errors.

The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
subjects range from end-user applications, programming tools, to games. Specifically:

\begin{itemize}
\Item CelarFTP\footnote{\url{http://celerftp.sourceforge.net/}}
and FileBunker\footnote{\url{http://filebunker.sourceforge.net/}} are two SWT desktop applications.
CelarFTP implements a simple FTP client based on Java and SWT UI library, and
FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.

\Item  AnyEdit\footnote{\url{http://andrei.gmxhome.de/anyedit/}}, FileSync4Eclipse\footnote{\url{andrei.gmxhome.de/filesync/}}, and
EclipseRunner\footnote{\url{http://eclipserunnerplugin.googlecode.com/}} are three popular eclipse plugins.
AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
FileSync4Eclipse is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.

\Item  S3dropbox\footnote{\url{http://s3dropbox.googlecode.com}} and SudokuPuzzleSolver\footnote{\url{http://sudokupuzzlesol.sourceforge.net/}}
are two Swing desktop applications. S3dropbox implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
computes Sodoku solutions efficiently using mutlithreading execution.

\Item  MyTracks\footnote{\url{http://code.google.com/p/mytracks/}}, Fennec\footnote{\url{http://www.mozilla.org/en-US/mobile/}},
and SGTPuzzles\footnote{\url{http://chris.boyle.name/projects/android-puzzles}} are three Android applications.
MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
interfaces to visualize them on Google Maps. Fennec, developed by Mozilla, is the Mozilla
Firefox web browser for mobile devices. SGTPuzzles is a small logic single-player game.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 \hline
 CelarFTP (3.0 alpha) &  2293 &  20 &  165  \\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.1.0) &  3101 &  48 &  354\\
 \hline
 FileSync (1.4.0)&  7374 &  36 &  510 \\
 \hline
 AnyEdit (2.4.0)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 Sudoku Solver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
 \hline
 MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6.2)&  20297 &  143 &  1374  \\
\hline
 Eclipse plugin development (3.6.2)&  20297 &  143 &  1374  \\
\hline
Swing (1.6)&  20297 &  143 &  1374  \\
\hline
 Android (3.6)&  20297 &  143 &  1374  \\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{}.  Each program is analyzed
together with its dependent GUI framework, as listed in
the bottom table.} }
\end{table}

@@

We run our tool on each subject with three call graph construction
algorithms: RTA~\cite{}, 0-CFA, and 1-CFA~\cite{}.  When running
each call graph construction algorithm on Android applications, we
use two configurations: with and without taming reflection (Section~\ref{}).
$k$-CFA ($k >$ 1) algorithm
does not scale to large programs, and thus is not used in this experiment

SGTPuzzler is the only subject that uses native methods to interact with
underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
annotations after inspecting its source code. In addition, two subjects XXXX and XXX use a self-defined
way to interact with the GUI framework. In this experiment, none of the paper
authors was faimilar with the subjects; but we found it is quite easy
to add extra those annotations and heuristic filters and finished these
manual parts in less than 20 minutes.

@@

Table~\ref{table:results} show the errors in
our subject programs, and Table~\ref{table:filters} show
the effect of applying each heuristic filter.

\subsubsection{Errors in Multithreaded GUI}
\label{sec:errors}

characteristic of errors in various subjects

False positive rate, and why?

redundant rate

response

Swing

Swing is a single-threaded GUI toolkit, and is not thread-safe. 
As the official documentation states, all Swing code must be executed in the UI-thread and
invoking Swing code from multiple threads risks thread interference or memory-consistency errors.

Since Swing does not provide any run-time checks for invalid thread access and, most of the time,
programmers can get away with an apparently ``well behaved'' Swing GUI that actually breaks the
single-thread rule.

Example in Swing
\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
/* In class: com.tomczarniecki.s3.gui.DeleteBucketAction */
59.private void deleteBucket() \{
60.    executor.execute(new Runnable() \{
61.        public void run() \{
62.            try \{
63.                controller.deleteCurrentBucket();
64.            \} catch (Exception e) \{
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \}
68.       \}
69.    \});
70.\}

77.private void deleteError() \{
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\}
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
potential invalid thread error reported by our tool
in the S3dropbox Swing application. The error occurs when
the invocation of \CodeIn{deleteCurrentBucket} at line 63 throws
an exception, which lead to the \CodeIn{deleteError} method
access a Swing GUI object \CodeIn{display} at line 79 from
a non-UI thread. This error has been confirmed by S3dropbox developers.
}} %\vspace{-5mm}
\end{figure}

Example in  Eclipse plugin
\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
179.private void initializeResourceChangeListener() \{
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \{
181.      public void resourceChanged(IResourceChangeEvent event) \{
182.        refresh();
183.      \}
184.  \}, IResourceChangeEvent.POST\_CHANGE);
185.\}

414.public void refresh() \{
415.  getViewer().refresh();
416.\}
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
potential invalid thread error reported by our tool
in the EclipseRunner plugin. The \CodeIn{IResourceChangeListener} object
added at line 180 is invoked by a non-UI thread, and the
callback method \CodeIn{resourceChanged} calls the \CodeIn{refresh}
method at line 414. However, the \CodeIn{refresh} method
directly accesses the GUI objects (at line 415) and triggers the error.
This error has been reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

@@

\subsubsection{Comparison with a Straightforward Approach}
\label{sec:straightforward}

As we mentioned in Section~\ref{sec:finding}, a standard way to avoid
invalid thread access errors is to wrap every GUI access code
with message passing methods (i.e., the safe methods). Thus, a
straightforward way to detect potential invalid error
is to check every method to determine whether all GUI-accessing code
is probably wrapping by safe methods. This approach
issues a warning for every violation. 
%If not, this approach issues warnings.

We implemented this straightforward approach and experimentally compared its
effectiveness with the technique presented in Section~\ref{}.
The far right column in Table~\ref{table:results} shows its result.
The results show that this straightforward approach can identified every
error as our technique does, but issues a tremendous number of false
positives. The primary reason is that this simple approach
does not globally reason about calling relationship between
threads, UI-accessing methods, and safe methods, thus it often incorrectly
classifies GUI accessing code which will never be executed
in a non-UI thread as errenous. Furthermore, our technique
outputs a method call chain in the error report, which can help
developers understand how an invalid thread access error is triggered.

@@

\subsubsection{Call Graph Construction Algorithms}
\label{sec:reflectionaware}

We compare three call graph construction algorithms, RTA, 0-CFA, and 1-CFA,
in our experiments. As shown in Table~\ref{table:results},  XXX found
more errors with less warnings than the XXX and XXXX algorithms. This
is because RTA and 0-CFA do not consider the context XXX, and it may
mix the same methods called by different callers. Although the call graphs
built by 1-CFA are significantly larger, XXX, the algorithm still runs
in a practical amouont of time as presented in Section~\ref{}. For example,
our tool finished building the call graph for the largest subject (xxx)
within xxx minutes.

The results in Table~\ref{table:results} also shown that using a reflection-aware
call graph construction algorithm is critical in finding errors in Android
applications. None of the errors in the studied Android applications
can be found by using normal call graph construction algorithms, because their 
limitation in handling reflection.

@@

\noindent \textbf{\textit{Summary.}} XX The 1-CFA call graph construction
algorithm is more effective in finding errors. XXX. Our reflection-aware call
graph construction algorithm is useful to find errors in
Android applications.

\subsubsection{Heuristic Filters}
\label{sec:filters}

We measure the effectiveness of the proposed heuristic filters of
Section~\ref{} via the number of removed warnings.

Table~\ref{table:filters} tabulates the results. The results show that
our technique outputs thousnads of warnings for each subject, due to
the conservative nature of static analysis.  However, the
set of proposed heuristic filters are highly effectively. They
 reduce the false positive numbers and redundant warnings by up to a factor of
XXX. Specifically, filters $XX_i$ and $XX_j$  identified xx\% of
the warnings as likely false positives, and filters $YY_i$
and $YY_j$ identified YY\% of the warnings as redundant warnings.
We further manually check each filtered warning, and found no
real errors have been removed.

@@

\noindent \textbf{\textit{Summary.}} Although a static analysis may
issue false postivies or redundant reports, a set of well-designed
heuristics can still remove most of them.
Heuristic filter, effective.

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|}
\hline
 Program  & \#Warning & \#Warning & \#Warning & \#Warning \\
 (version) & $F_1$ & $F_2$ & $F_3$&$F_4$ \\
\hline \hline
\multicolumn{5}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters (Section~\ref{}). Column ``\#Warning $F_i$''
represents the number of remaining warnings after applying
filters 1 -- $i$, and the number of last column is taken
from Table~\ref{} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
\end{table}

@@

Our experiments also demonstrate that our approach has good scalability.
Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
the largest subject our approach can analyze and detect errors has
over XXX LOC, xx classes, and xxx methods.

@@

There are two major threats to validity in our evaluation. 
The major threat is the degree to which the subject programs
used in our experiment are representative of true practice.
In our evaluation, the studied subjects were selected with a bias towards popularity from
three open-source repositories. Another threat is that we only employed three
well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
in our implementation. It is still unknown whether using other 
call graph construction algorithms such XFA~\cite{} may achieve better results.

@@

Our technique is limited in two aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
such threads. Second, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false positive
rate is ongoing work.

@@

\subsubsection{Experimental Conclusions}
Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype

 Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place. That is why there is a Worker interface in this project

>>>>

We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
market as evaluation subjects. To choose subjects for each supported GUI framework,
we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then select subjects based on the following
criterias. First, the subject must be a multithread GUI application, not
an open library. Second, the subject must undergone at least two years of active development,
and is listed in the first 3 results pages based on popularity. This permits us
to exclude many pre-mature subjects that may contain obvious errors.

The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
subjects include end-user applications, programming tools, and games. Specifically:

\begin{itemize}
\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
SWT desktop applications.
CelerFTP implements a simple FTP client based on Java and SWT UI library, and
FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.

\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.

\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
are two Swing desktop applications. S3dropbox implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
computes Sodoku solutions efficiently using mutlithreading execution.

\Item  MyTracks~\cite{mytracks}, Fennec~\cite{fennec},
and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
interfaces to visualize them on Google Maps. Fennec, developed by Mozilla, is the Mozilla
Firefox web browser for mobile devices. SGTPuzzles is a small logic single-player game.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 \hline
 CelerFTP (3.0 alpha) &  2293 &  20 &  165  \\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.1.0) &  3101 &  48 &  354\\
 \hline
 FileSync (1.4.0)&  7374 &  36 &  510 \\
 \hline
 AnyEdit (2.4.0)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 Sudoku Solver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
 \hline
 MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6.2)&  xxxxx &  xxx &  xxxx  \\
\hline
 Eclipse plugin development (3.6.2)&  xxxxx &  xxx &  xxxx  \\
\hline
Swing (1.6)&  xxxxx &  xxx &  xxxx  \\
\hline
 Android (3.6)&  xxxxx &  xxx &  xxxx  \\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its dependent GUI framework, as listed in
the bottom table.} }
\end{table}

@@

We run our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on Android applications, we
use two configurations: with and without the reflection-aware transformation
(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to large programs.

We inspect the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns are implemented.
We found SGTPuzzler is the only subject that uses native methods to interact with
underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
annotations for it. Also two subjects XXXX and XXX employ a self-defined
way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
method in the XXX subject first checks whether the current thread is the UI-thread, and
then determines whether to direct access a GUI object or wrap the code with
message passing. We add XX heuristic filtering rules for those methods, to indicate
that they are safe to be invoked from any thread. In this experiment, none of the paper
authors was faimilar with the subjects; but we found it is quite easy
to add extra those annotations and heuristic filters and finished these
manual parts in less than 20 minutes.

@@

%Table~\ref{table:results} show the errors in
%our subject programs, and Table~\ref{table:filters} show
%the effect of applying each heuristic filter.

\subsubsection{Errors in Multithreaded GUI Applications}
\label{sec:errors}

Table~\ref{table:results} tabulates the results of running our
tool with three different call graph construction algorithms
on the subject programs. From these results, we can see our
tool found real errors from each subject on all the 
supported GUI frameworks. The results vary slightly according
to the specific call graph algorithm used. In general, using
the 1-CFA algorithm finds most errors (XXX in total) with least
warnings (XXX in total). The tradeoffs of using other
algorithms will be explained in Section~\ref{sec:reflectionaware}.

We further examined the detailed results for each subject.
Among xxx warnings issued by using the 1-CFA algorithm, xxx
are false positives, xxx are redundant:
they have the same causes as the rest xxx warnings. (XXX why there
are FP and redundant warnings?)

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
/* In class: com.tomczarniecki.s3.gui.DeleteBucketAction */
59.private void deleteBucket() \{
60.    executor.execute(new Runnable() \{
61.        public void run() \{
62.            try \{
63.                controller.deleteCurrentBucket();
64.            \} catch (Exception e) \{
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \}
68.       \}
69.    \});
70.\}

77.private void deleteError() \{
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\}
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
potential invalid thread access error reported by our tool
in the S3dropbox Swing application. The error occurs when
the method \CodeIn{deleteCurrentBucket} invoked at line 63 throws
an exception, which leads method \CodeIn{deleteError} to
access a Swing GUI object \CodeIn{display} at line 79 from
a non-UI thread. This error is previously-unknown, and has been confirmed by the S3dropbox developers.
}} %\vspace{-5mm}
\end{figure}

Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
two real errors our tool has found. Figure~\ref{fig:swingerror}
shows a potential invalid thread access error in the S3dropbox
program. This error happens when the \CodeIn{deterCurrentBucket}
method at line 63 throws an exception. This error can be hard to
detect by testing, since the test must  execute that specific exception-handling
path. We reported this error to the S3dropbox developers. Tom Czarniecki,
a key developer of S3dropbox confirmed this potential single-thread
violation. He mentioned that the S3dropbox project has already
used certain design patterns and practice to avoid such violations (e.g.,
actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
but they still overlooked  the reported code snippet.

Another reason of missing this violation is because some GUI frameworks like Swing
do not provide any run-time checks for invalid thread access. Most
of the time, programmers can get away with an apparently ``well behaved'' Swing
GUI that actually breaks the single-thread rule. However, As clearly
indicated in the official documentation, Swing is a single-threaded GUI
toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
invoking Swing code from multiple threads risks thread interference
or memory-consistency errors, particularly in the multi-core era.

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt} 
/* com.eclipserunner.views.impl.RunnerView */
179.private void initializeResourceChangeListener() \{
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \{
181.      public void resourceChanged(IResourceChangeEvent event) \{
182.        refresh();
183.      \}
184.  \}, IResourceChangeEvent.POST\_CHANGE);
185.\}

414.public void refresh() \{
415.  getViewer().refresh();
416.\}
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
potential invalid thread access error reported by our tool
for the EclipseRunner plugin. In Eclipse, the
callback method \CodeIn{resourceChanged} at line 181
is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
happens. However, the \CodeIn{refresh} method directly accesses
GUI objects (refresh the view at line 415) without any
protection and thus triggers the error.
This error has been reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

Figure~\ref{fig:pluginerror} shows an error found in the EclipseRunner
plugin. This error is event-related. It happens when a 
\CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
method at line 415 to update the user interface. In EclipseRunner
, the \CodeIn{refresh} method has been
called by XXX different methods in non-UI threads. Thus, our
tool issues XXX separate warnings for each caller method to indicate
different ways to trigger this error, despite that all these xxx warnings
acutally have the same error cause.

As reflected in our experiments, we found GUI developers have already
used design patterns, runtime checks, and testing to avoid violating
the single-thread rule. However, due to the huge space of
possible UI interactions, potential
invalid thread access errors still exist in many corner cases and
can be hard to find. Thus, a static analysis as presented in this paper
would be useful.

@@

\subsubsection{Comparing to a Straightforward Approach}
\label{sec:straightforward}

As we mentioned in Section~\ref{sec:finding}, a standard way to avoid
invalid thread access errors is to wrap every GUI access code
with message passing methods (i.e., the safe methods). Thus, a
straightforward way to detect potential invalid error
is to check every method to determine whether all GUI-accessing code
is probably wrapping by safe methods. If not, this approach
issues a warning for every violation. 
%If not, this approach issues warnings.

We implemented this straightforward approach and experimentally compared it
with the technique presented in Section~\ref{sec:technique}.
The far right column in Table~\ref{table:results} shows the results.
The results show that this straightforward approach can identified every
error as our technique does, but leads to a tremendous number of false
positives and redundant warnings. The primary reason is that this simple approach
does not globally reason about calling relationship between
threads, UI-accessing methods, and safe methods, thus it often incorrectly
classifies GUI accessing code which will never be executed
in a non-UI thread as errenous. Furthermore, our technique
outputs a method call chain in the error report, which can help
developers understand how an invalid thread access error is triggered.

@@

\subsubsection{Comparing Call Graph Construction Algorithms}
\label{sec:reflectionaware}

We next compare three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  XXX found
more errors with less warnings than the XXX and XXXX algorithms. This
is because RTA and 0-CFA do not consider the context XXX, and it may
mix the same methods called by different callers. Although the call graphs
built by 1-CFA are significantly larger, XXX, the algorithm still runs
in a practical amouont of time. For example,
our tool finished building the call graph for the largest subject (xxx)
within xxx minutes.

The results in Table~\ref{table:results} also show that using a reflection-aware
call graph construction algorithm is critical in finding errors in Android
applications. None of the errors from the Android applications
can be found by using normal call graph construction algorithms, due to
their limitation in handling platform-specific reflections. Without
replacing the reflection calls with explicit object creation instructions,
a call graph construction algorithm will
conclude that no GUI object has been created, and thus miss many UI-related
edges in the resulting graph.

@@

\noindent \textbf{\textit{Summary.}} Using the 1-CFA call graph construction
algorithm is more effective in finding errors, and our reflection-aware call
graph construction algorithm is critical to find errors on
Android applications.

\subsubsection{Evaluating Heuristic Filters}
\label{sec:filters}

We measure the effectiveness of the proposed heuristic filters of
Section~\ref{sec:heuristic} via the number of removed false positives and
redundant warnings.

Table~\ref{table:filters} tabulates the results. Although
our static analysis outputs thousands of warnings for each
subject, the proposed heuristic filters effectively reduces
the number. On average, they
 reduce the false positive numbers and redundant warnings by up to a factor of
XXX. Specifically, filters $XX_i$ and $XX_j$  identified xx\% of
the warnings as likely false positives, and filters $YY_i$
and $YY_j$ identified YY\% of the warnings as redundant warnings.
We further manually check each filtered warning, and found no
real errors have been removed.

@@

\noindent \textbf{\textit{Summary.}} Although a static analysis may
issue false postivies or redundant reports, a set of well-designed
heuristics can still remove most of them.
%Heuristic filter, effective.

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.30\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 Subject & Before & \#Warning & \#Warning & \#Warning & \#Warning& \#Warning \\
 Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
represents the number of remaining warnings after applying
filters 1 -- $i$, and the number of last column is taken
from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
\end{table}

@@

Our experiments also demonstrate that our approach has good scalability.
Together with all dependent library code, our tool has analyzed
XXX LOC in total  XXX LOC in the largest program.
%Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
%the largest subject our approach can analyze and detect errors has
%over XXX LOC, xx classes, and xxx methods.

@@

There are two threats to validity in our evaluation. 
The major threat is the degree to which the subject programs
used in our experiment are representative of true practice.
In our evaluation, the studied subjects were selected with a bias towards popularity from
three open-source repositories. Another threat is that we only employed three
well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
in our implementation. It is still unknown whether using other 
call graph construction algorithms such as XTA~\cite{xta} may achieve better results.

@@

Our technique is limited in two aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those threads created before a GUI is launched.
Second, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false positive
rate is ongoing work.

@@

\subsubsection{Experimental Conclusions}

Invalid thread access errors significantly affect the usability of
a GUI application, but can be subtle to find. In practice, programmers
have designed practices and patterns to avoid such errors in the first
place, but can easily overlook corner cases like exception-handling
methods.

The technique presented in this paper offers a promising solution.
Compared with the straightforward approach to check every
GUI accessing code isolatedly, our technique produces significantly
less warniings. The reflection-aware call graph construction algorithm
is critical in detecting errors for Android programs, and our
proposed heuristic filtering rules are useful in reducing programmers'
burden to inspect the output result.

%Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype

% Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place. That is why there is a Worker interface in this project
